### 2018-03-16 paper/5-implementations.tex
Polish S5.1

\Make processes keys in a linear order based on a topological sort
(see~\S\ref{sec-concurrency} for parallel \Make). For each key, it builds it if
it is older than any of its dependencies. We can express this in our framework
as follows. We capture the persistent information stored by \Make as a pair
\hs{(@@modTime,}~\hs{now)} comprising the \emph{file modification time} function
\hs{modTime}~\hs{::}~\hs{k}~\hs{->}~\hs{Time} and the current time \hs{now}.

@@

The helper function \hs{topological}, which we describe later, calls
\hs{process} on every \hs{key} in the topological order, providing the list of
its dependencies \hs{deps} and the action \hs{act} to compute the resulting
value if it needs to be rebuilt. To determine if the \hs{key} is \hs{dirty},
\hs{process} compares its modification time with those of its dependencies. If
\hs{key} needs to be rebuilt, the associated action \hs{act} is executed and
the obtained result is stored, along with an updated file modification
timestamp. The \hs{make} build system, as described, captures the essence of
\Make in a clear and precise manner.

>>>>

\Make processes keys in a linear order based on a topological sort
(see~\S\ref{sec-concurrency} for parallel \Make). For each key, it builds it if
it is older than any of its dependencies. To express \Make in our framework,
we capture the persistent information it stores by a pair
\hs{(@@modTime,}~\hs{now)} comprising the \emph{file modification time} function
\hs{modTime}~\hs{::}~\hs{k}~\hs{->}~\hs{Time} and the \emph{current time} \hs{now}.
Setting aside the explicit manipulation of file modification times, which in
reality is taken care of by the file system, the \hs{make} build system defined
below captures the essence of \Make in a clear and precise manner.

@@

\noindent
The helper function \hs{topological}, which we describe below, calls
\hs{process} on every \hs{key} in the topological order, providing the list of
its dependencies \hs{deps} and the action \hs{act} to compute the resulting
value if it needs to be rebuilt. To determine if the \hs{key} is \hs{dirty},
\hs{process} compares its modification time with those of its dependencies. If
the \hs{key} needs to be rebuilt, the action \hs{act} is executed and the
obtained result is stored, along with an updated file modification timestamp.
